A pipeline to analyse time-course gene expression data

### 2019-05-08 scripts/manuscript.Rmd
Manuscript is now compiled in PDF format

# Reorder genes on condition, time, and replicate
ord = order(
  meta$Group,
  meta$Timepoint,
  meta$Replicate)
data = data[, ord]
meta = meta[ord, ]

@@

```{r echo=FALSE}
kable(head(log_fold_change_timepoints[,
colnames(log_fold_change_timepoints)[1:5]]))
```

@@

colnames(pathways) = c("Pathway", "Percentage", "Adj. p-value")
pathways["Percentage"] = pathways["Percentage"] * 100
kable(pathways[1:10, ], "html", escape=F, digits=4) %>%
    kable_styling("striped", full_width=TRUE) 
```

@@

go_terms_enriched = go_terms_enriched[
    order(go_terms_enriched[, "resultFisher_padj"]), ]

kable(go_terms_enriched[1:15, ], "html", escape=F, digits=4) %>%
    kable_styling("striped", full_width=TRUE) 
```

>>>>

# Reorder genes on condition, time, and replicate
ord = order(
  meta$Group,
  meta$Timepoint,
  meta$Replicate)
variance_filtered_data = variance_filtered_data[, ord]
meta = meta[ord, ]

@@

```{r echo=FALSE}
kable(
    head(log_fold_change_timepoints[, colnames(log_fold_change_timepoints)[1:5]]),
    format = "latex")
```

@@

colnames(pathways) = c("Pathway", "Percentage", "Adj. p-value")
pathways["Percentage"] = pathways["Percentage"] * 100
kable(pathways[1:10, ], "latex", escape=F, digits=4) %>%
    kable_styling("striped", full_width=TRUE) 
```

@@

go_terms_enriched = go_terms_enriched[
    order(go_terms_enriched[, "resultFisher_padj"]), ]
colnames(go_terms_enriched) = c("GO ID", "Description", "Annotated",
"Significant", "Expected", "P-value", "adj. p-value")

kable(go_terms_enriched[1:15, ], "latex", escape=F, digits=4)  %>%
    kable_styling("striped", full_width=TRUE) 
```
